# Data sources

## Yahoo Finance

- The crypto and traditional stocks data  will be obtained by Yahoo Finance Website [YH Finance](https://finance.yahoo.com)

- We need following two packages to import data.

  - quantmod
  
  - TTL

Here we show the code of extracting the Bitcoin Data of the latest three days.

    install.packages('quantmod')
    install.packages('TTR')
    library('TTR')
    library('quantmod')
    df_btc <- getSymbols('BTC-USD',src='yahoo',auto.assign=FALSE)
    tail(df_btc,3)

```{r include = TRUE}
df_btc <- getSymbols('BTC-USD',src='yahoo',auto.assign=FALSE)
tail(df_btc,3)
```

## Google Trend

To quantify the social impact of the cryptos, we use Google Trend as the measurement and retrieve Google Trends data via `gtrendsR` package.

The `gtrendsR` package is on CRAN and can be installed via
    
    install.packages("gtrendsR")

Here we show the code of retrieving and displaying the Google Trend 'interest over time' data for the keyword 'Bitcoin' in the United States.

    install.packages("gtrendsR")
    library(gtrendsR)
    Bitcoin_US_trend <- gtrends(c("Bitcoin"), geo = c("US"))
    print(tail(Bitcoin_US_trend$interest_over_time,3))

```{r}
Bitcoin_US_trend <- gtrends(c("Bitcoin"), geo = c("US"))
print(tail(Bitcoin_US_trend$interest_over_time,3))
```

