# Data sources

- Xuan Lian is responsible for collecting the data.

## Yahoo Finance API

- The crypto and traditional stocks data  will be obtained by Yahoo Finance Website [YH Finance](https://finance.yahoo.com)

- We need following two packages to import data.

  - quantmod
  
  - TTL

Here we show the code of extracting the Bitcoin Data of the latest three days.

    install.packages('quantmod')
    install.packages('TTR')
    library('TTR')
    library('quantmod')
    df_btc <- getSymbols('BTC-USD',src='yahoo',auto.assign=FALSE)
    tail(df_btc,3)

```{r include = TRUE}
df_btc <- getSymbols('BTC-USD',src='yahoo',auto.assign=FALSE)
tail(df_btc,3)
```



## Google Trend API

To quantify the social impact of the cryptos, we use Google Trend as the measurement and retrieve Google Trends data via `gtrendsR` package.

The `gtrendsR` package is on CRAN and can be installed via
    
    install.packages("gtrendsR")

Here we show the code of retrieving and displaying the Google Trend 'interest over time' data for the keyword 'Bitcoin' in the United States.

    install.packages("gtrendsR")
    library(gtrendsR)
    Bitcoin_US_trend <- gtrends(c("Bitcoin"), geo = c("US"))
    print(tail(Bitcoin_US_trend$interest_over_time,3))

```{r}
Bitcoin_US_trend <- gtrends(c("Bitcoin"), geo = c("US"))
print(tail(Bitcoin_US_trend$interest_over_time,3))
```

## CoinMarketCap 

We are also interested in the data of the market cap of cryptocurrencies, so we will also use CoinMarketCap website to get historical market cap data of cryptocurrencies.

We will use `rvest` package to get the information from the website. We are interested in the yearly market cap data, so we get the historical snapshot at December 31th from 2016 to 2021 for the top 20 market cap cryptocurrencies and ignore the others.

    base_url = 'https://coinmarketcap.com/historical/'
    for(year in seq(2016,2021)){
      url = paste0(base_url,year,'1231')
      dt = read_html(url) %>% html_table(fill = TRUE)
      dt = dt[3][[1]] %>% 
        select(Symbol, `Market Cap`) %>%
        mutate('year' = year) %>%
        slice_head(n=20)
    if(year == 2016){crypto_market_cap = as_tibble(dt)}
    else{crypto_market_cap = rbind(crypto_market_cap,dt)}
      }

```{r}
base_url = 'https://coinmarketcap.com/historical/'

for(year in seq(2016,2021)){
  url = paste0(base_url,year,'1231')
  dt = read_html(url) %>% html_table(fill = TRUE)
  dt = dt[3][[1]] %>% dplyr::select(Symbol, `Market Cap`) %>%
    mutate('year' = year) %>%
    slice_head(n=20)
  if(year == 2016){
    crypto_market_cap = as_tibble(dt)
  }
  else{
    crypto_market_cap = rbind(crypto_market_cap,dt)
  }
}
print(head(crypto_market_cap))
```

