# Missing values

We are going to use adjusted closing price to compare the behavior between the traditional stocks and cryptocurrencies.

For traditional stocks, due to the limitation of trading dates, OHLCV data on non-trading dates will be missing compared to cryptocurrencies, and we choose to use previous data to fill in.

We will try to figure out the problem using the daily adjusted closing price of Bitcoin and NASDAQ 100 from 2016 to 2021, here is the sample of our origin data.

```{r include = TRUE}
df_ndx <- getSymbols('^NDX',src='yahoo',auto.assign=FALSE)
date_seq = seq(as.Date("2015/12/31"), as.Date("2021/12/31"), "days")
df_ndx_1 = df_ndx[date_seq]$NDX.Adjusted
df_btc_1 = df_btc[date_seq]$`BTC-USD.Adjusted`
df_1 = df_btc_1 %>% merge(df_ndx_1)
head(df_1,5)
```

Here we plot the missing values in year 2016.

```{r}
df_2 = as_tibble(df_1) %>% 
  cbind(date = date_seq) 
tidy_df_1 = df_2 %>%
  slice(1:365) %>%
  gather(key, value, -date) %>% 
  mutate(missing = ifelse(is.na(`value`), "yes", "no")) 
ggplot(tidy_df_1, aes(x = key, y = date, fill = missing)) +
  geom_tile(color = "white") + 
  scale_fill_viridis_d() +
  scale_y_date(date_breaks = '1 month') +
  labs(title = 'Missing values in year 2016') +
  theme_bw()
df_2 = df_2 %>%
  column_to_rownames('date')
plot_missing(df_2)
```

And we will use last non-missing observation carried forward to fill missing values

```{r}
df_no_missing = df_2 %>%
  column_to_rownames('date') 
df_no_missing = setnafill(df_no_missing,'locf')
head(df_no_missing)
```